Reliable analytic approximation of pseudo-$\cl$ covariances

### 2019-05-17 draft/paper.tex
added paragraph about foregrounds

In order to generate the simulated $\cl$ we computed the correlations between
Gaussian fields obtained from a fiducial power spectra. The covariance
matrices were obtained from 20000 simulations, for the band powers determined
by the fraction of sky observed and the maximum band power we were able to
recover the fiducial power spectra for; i.e. $\sim 2 \times 512$. This
corresponds to $l_{\mbox{bpw}} = 1023$. For the lecture of the sky maps and
masks we used \textit{HEALPix}\footnote{\url{https://healpix.jpl.nasa.gov/}}
and
\textit{NaMaster}~\cite{2018arXiv180909603A}\footnote{\url{https://github.com/LSSTDESC/NaMaster}}
for the computation of the pseudo-$\cl$ and the covariances. Our code is
publicly available~\footnote{\url{https://github.com/damonge/PCLCovariance}}.

>>>>

In order to generate the simulated $\cl$ we computed the correlations between
Gaussian fields obtained from a fiducial power spectra. The covariance
matrices were obtained from 20000 simulations, for the band powers determined
by the fraction of sky observed and the maximum band power we were able to
recover the fiducial power spectra for; i.e. $\sim 2 \times 512$. This
corresponds to $l_{\mbox{bpw}} = 1023$. For the lecture of the sky maps and
masks we used \textit{HEALPix}\footnote{\url{https://healpix.jpl.nasa.gov/}}
and
\textit{NaMaster}\footnote{\url{https://github.com/LSSTDESC/NaMaster}}~\cite{2018arXiv180909603A}
for the computation of the pseudo-$\cl$ and the covariances. Our code is
publicly available~\footnote{\url{https://github.com/damonge/PCLCovariance}}.

The same results are obtained even in the presence of foregrounds. In
particular, we tested the case with 100 foregrounds both at low scales and
large scales, adding a mock power spectra computed as $\clf = A (l +
1)^{\beta}$. Here, $A$ was fixed so that the ratio of the foreground power
spectra and the theoretical one ($\clth$) was $\clf/\clth = 0.1$ at $l=400$
and $\beta$ was randomly chosen from $U[-3, -1)$ for large scale effects and
fixed to $\beta = 0$ for small scale ones.
